\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin= 2.5 cm]{geometry}

\title{Epoch Bylaws}
\date{}
\author{The Epoch Board}
\begin{document}

\maketitle
\section*{Definition of Terms}
\begin{enumerate}
    \item The key words “MUST”, “MUST NOT”, “REQUIRED”, “SHALL”, “SHALL NOT”, “SHOULD”, “SHOULD NOT”, “RECOMMENDED”, “MAY”, and “OPTIONAL” in this document are to be interpreted as described in the IETF's RFC 2119, excluding the changes made in RFC 8174 (both UPPERCASE and lowercase usage of the key words have the defined special meanings).
\end{enumerate}
\section{Purpose}
\begin{enumerate}
    \item The purpose of Epoch is to create a student-run cluster for the education of Illinois Mathematics and Science Academy ("IMSA") students in machine learning and other computationally intensive fields.
\end{enumerate}
\section{Management Divisions}
\begin{enumerate}   
    \item Epoch must consist of three Management Divisions: Technical,  Relations, and Business.
    \item Technical Division's main purpose shall be to build, configure, manage, and secure the cluster.
    \item Relations Division's main purpose shall be to conduct interactions with other groups within IMSA, including administration and other student groups.
    \item Business Division's main purpose shall be to raise funds and to conduct relations with individuals and groups outside IMSA.
    \item Each Division must be allowed to operate with a high level of autonomy when working toward  their goals, and must be able to adopt their own bylaws and policies as long as they are compatible with this document.
    \item Within this document, some rules may be designed to interact with a Division's bylaws, and shall have no effect until that Division adopts the implementing bylaws.
    \item The enumeration of purposes within this section shall not be construed to limit a Division's goals and abilities.
    \item The enumeration of purposes within this section shall not be construed to limit Epoch's goals and abilities. Additionally, elements of Epoch may be unaffiliated with \textit{any} of the Epoch Management Divisions.
    
\end{enumerate}

\section{Membership and Board Structure}
\begin{enumerate}
    \item Membership shall be open to all members of the IMSA community who have a interest in the computational and data sciences. 
    \item Members must be in good standing with IMSA administration and the community, unless an exception is made by the Board with a super-majority vote. This exception shall be made on a case-to-case basis.
    \item Membership shall be granted through request at any meeting, via email, or through joining the Epoch chat server.
    \begin{enumerate}
        \item While this chat server is currently on the Discord platform, this platform may be changed in the future. In the event that it is, the Board shall notify members through by broadcasting a Notice of Platform Change to all members of the previous chat platform, and provide a minimum one week transition period before the previous chat platform may be considered deprecated.
    \end{enumerate}
    \item Epoch must have a Board of Directors ("Board"), consisting of a Chief Executive Officer (CEO), a Chief Technical Officer (CTO), a Chief Systems Officer (CSO), a Systems Head Admin (SHA), a Chief Relations Officer (CRO), Chief Financial Officer (CFO), and a Chief Curriculum Officer (CCO).
    \begin{enumerate}
        \item While the Board is only defined as the Main Board and does not include Shadow Board members, the Main Board members may choose to involve their shadows in Board actions. 
    \end{enumerate}
    \item The CTO, CSO, and SHA shall be affiliated with the Technical Division, the CRO and CCO shall be affiliated with the Relations Division, and the CFO shall be affiliated with the Business Division. The CEO, as head of Epoch, must be unaffiliated with any subdivision.
    \item The officers who are affiliated with a division shall be in charge of leading that division.
    \item Each officer on the Board must choose a Shadow by the end of the first quarter. This Shadow need not be somebody highly qualified in the field, but somebody who is willing to learn the necessary information. Enthusiasm and consistency should be rewarded.
    \begin{enumerate}
        \item Extensions may be granted by a supermajority vote of the Board.
    \end{enumerate}
    \item Shadows shall be appointed by the Board officer with the advice and consent of the full Board and the Officer's division. The Shadow CEO shall be chosen by the current CEO and be certified by a vote of all active Epoch student members. A Shadow must be a Sophomore or Junior when they are instated.
    \item If a officer of the Board leaves Epoch (or graduates from IMSA), that officer's Shadow shall take over his/her role if the officer's Division provides a successful vote of confidence in the Shadow, or in the case of the CEO, a successful vote from all active Epoch Board and Shadow Board members. In the case that the vote fails, a new member shall be chosen by the Board and the voting process shall repeat.
    \item In Epoch Board meetings, each division shall have an assigned number of votes. The Technical division shall have three (3) votes, with each of the CTO, CSO, and SHA allocated one (1) vote. The business team shall have one (1) vote, with the CFO allocated one (1) vote. The relations team shall have two (2) votes, with each of the CEO and CCO assigned one (1) vote. The CEO shall have one (1) vote. In the event that a Board position cannot be filled, the remaining votes must be split evenly among the members of the division.
    \begin{enumerate}
        \item In the event of a tie, the decision with the vote of the senior officer in that division shall break the tie. Extend this concurrently to the shadow Board of that division and finally, the CEO.
    \end{enumerate}
    \item The Board must have the funding, resources and authority appropriate to discharge its responsibilities, and shall, as it deems appropriate and at the expense of Epoch, engage and obtain advice and assistance from outside advisors. 
\end{enumerate}
\section{Meetings}
\begin{enumerate}
    \item Epoch must hold a general meeting at least once every two weeks during the school year, with an agenda agreed upon beforehand by the Board of Directors. This time can be revised at any point in the year. Meetings shall take place on the IMSA campus or via a digital platform, in areas accessible to all students.
    \item Epoch general meetings shall be announced at least 48 hours in advance, and notice of meetings and any record thereof shall be posted to the Epoch chatroom and website.
    \item Divisions may choose to have meetings whenever they choose in places accessible to all members of that Division.
    \item Epoch Board or the leadership of a Division may choose to hold a closed meeting to discuss on sensitive topics. It is expected that if a meeting is closed to an officer or shadow officer, that officer should not directly join the meeting. However, this does not bar them from asking questions.
\end{enumerate}
\section{Subcommittees, Subteams, and Classes}
\begin{enumerate}
    \item The Board may authorize subteams or subcommittees for any purpose necessary.
    \item For the purpose of educating and training Epoch members and facilitating discussion and research, Epoch members may create classes in fields pertinent to Epoch operations with Board approval. The Board may invite guest lecturers. These classes shall be supervised and coordinated by those with extensive knowledge in the field.
    \item Project teams, subcommittees, and classes may request funds and materials from the Business Division. Requests shall go to the CFO $\rightarrow$ shadow CFO $\rightarrow$ CEO $\rightarrow$ shadow CEO in that order of priority. If it is not possible for any of the members to approve requests, a purchase may not be made at that time, unless the Epoch staff advisor provides written approval for the expense.
    \item Subteams and subcommittees may operate under their own charters, provided that they do not conflict with this document.
    \item Subteams and subcommittees may add their own advisors which may not necessarily be Epoch advisors.
    \item On receiving their respective charters, subteams, subcommittees and classes shall be considered part of no Division, but they may petition to join a Division.
    \item At least once per semester, Epoch shall hold a meeting with Board, the heads of each subteam or subcommittee, and those responsible for running classes.
    \item Epoch recognises pre-existing agreements with the Education through Competition subteam, the Titan Scouting subteam, and the AI in Medicine subteam.
\end{enumerate}
\section{Procedure and Ethics}
\begin{enumerate}
    \item The CEO (or their designeee) shall chair all Board meetings.
        \item The supermajority of the Board members shall constitute a quorum for transacting official Board business. When members are unable to be physically present, they may fully participate by teleconference. The technology must enable Board members to hear the other member(s) not physically present and enable the member(s) not physically present to hear the Board discussion.
    \begin{itemize}
        \item Rulings passed without quorum are null and void.
    \end{itemize}
    \item Board meetings shall follow a predetermined agenda, if one exists, with the Board having the ability to add and remove items if needed.
    \item The Board shall not pass any ex post facto rulings.
    \item Due process shall be followed in all proceedings.
    \item Disputes within a Division shall be handled within that Division based on the Division's policies. If the dispute is between two members of different Division, a Board or Shadow Board officer from the unaffected Division or an unaffiliated Board or Shadow Board officer shall mediate. The CEO should often take this position as an impartial party.
    \item Board officers may take a sabbatical (where their Shadow or another designated Epoch member temporarily assumes their position) or resign their positions by writing a letter to the CEO. If an officer resigns, they may not apply to be reinstated until four weeks after the date which their resignation letter takes effect.
    \item If the Board loses trust in an officer, they can pass a motion of no confidence (the text of the motion including ``this body has no confidence in [name] fulfilling [his/her/their] duties as [position]'') with a formal Board vote to remove the officer from their position.
    \item All Epoch members shall follow all Epoch, IMSA, state, and federal rules, regulations, and laws when representing Epoch and shall hold themselves to a high moral standard. The Epoch Board may open investigations into any events involving Epoch that do not follow these standards.
    \item Any formal Board vote must pass with a supermajority among the Board.
    \item To open an investigation, Board shall pass a resolution outlining the scope of the investigation and appointing someone to build the case against those investigated. 
    \item Those investigated shall have the right to be informed of nature of the investigation, to review all evidence and confront all witnesses against him/her and to introduce his/her own evidence and witnesses, to obtain counsel within Epoch, to not bear witness against himself/herself, and not to be investigated twice for the same charges.
    \item For each investigation, a panel of two Board or Shadow Board members and one non-Board individual (potential panel members may recuse themselves) shall decide on the guilt and punishment of those accused. Punishments may range from a formal censure to a removal and ban from Epoch. In extreme cases, the results of an investigation and any evidence used may be forwarded to IMSA formal disciplinary officers. The outcomes of each case shall serve as precedence for future cases.
    \item If the panel decides on a guilty ruling against a Board member, it may also recommend his/her removal on ethics. If such a recommendation is made, the Board shall vote on it at its next meeting and a majority vote shall result on the member's removal.
    \item All non-confidential materials of an investigation shall be made available to Epoch members upon request.
\end{enumerate}
\section{Advisors}
\begin{enumerate}
    \item Epoch shall seek at least one faculty advisor to provide guidance and direction to Epoch members and assist in resolving any disputes.
    \item New advisors that are listed as Epoch advisors to administration shall be added with Board approval.
    \item The Technical Division may add official Technical Advisors (which are not necessarily Epoch advisors or even within the IMSA community) with the consent of the CTO and CSO, shall control the application process for this role, and may send out invites to apply.
    \item The Business Division may add official Business Mentors (which are not necessarily Epoch advisors or even within the IMSA community) with the consent of the CEO, shall control the application process for this role, and may send out invites to apply.
    \item The Board may approve official Education Advisors, responsible for reviewing classes and their curriculum, and providing help if necessary.
    \item If needed, the leadership of each Department may give temporary supervisor roles to those who hold the proper IMSA clearances.
\end{enumerate}
\section{System Administrators and the Cluster}
\begin{enumerate}
    \item As the construction of a secure student-run cluster is necessary to fulfill Epoch's purpose, the Technical Division shall set up a training and certification program for cluster hardware technicians and system administrators (sysadmins). These training and certification programs shall correspond with various professional certifications that are issued in the IT industry.
    \item The officers leading the Technical Division (CSO, CTO, SHA) shall be assigned the role of lead sysadmin and must thus be in charge of holding cluster root credentials.
    \begin{enumerate}
        \item Main Board members may choose to extend this designation to their shadows.
        \item The Technical Division may choose to extend this designation to other technical division members, contingent on the consent of a supermajority of the officers leading the Technical Division.
    \end{enumerate}
    \item Head sysadmins may send out communications to whoever it may concern dictating current technical objectives and what is needed to fulfill them. When the cluster is undergoing development, expansion, or upgrade, these communications must occur at least biweekly.
    \item Head sysadmins are in charge of managing credentials, and thus may certify other members of Technical Division to hold admin access to some systems and manage their permissions.
    \item Since much trust must be placed in sysadmins and they have the power to cause extreme harm to Epoch in unique ways, Technical Division shall implement vetting processes of those holding admin access, and both Technical Division and Board have the power to recall a system administrator's access privileges (including a head sysadmin) with a formal vote.
    \item Technical Division is in charge of distributing cluster access credentials and managing access. While the cluster is intended to be open for all who need it, head sysadmins may deny a potential user credentials if they deem that the user poses a security or ethics risk. These denials shall be documented.
    \item Head sysadmins may revoke credentials whenever deemed necessary. These revokals shall be documented.
    \item Technical Division may restrict higher-risk aspects of the cluster and create systems to decide which members may gain access to those parts.
    \item Technical Division may create policies regarding the usage of the cluster.
    \item Technical Division may open ethics investigations as described in Section 6 into potential misuse of the cluster or security breaches.
    \item The enumeration of powers within this section shall not be interpreted to limit Technical Division's or its members' powers to  build, configure, manage, and secure the cluster.
\end{enumerate}
\section{Adoption and Amendment}
\begin{enumerate}
    \item These bylaws have been adopted by Board 1 (CEO JuWon Park, CTO Dev Singh, CSO Simone Angelov, CFO Archan Das, CCO Hamza Haq, and CRO Sage Owen) on August 5, 2020.
    \item These bylaws may be modified by a super-majority vote of all Board officers after a minimum 24-hour consideration period.
\end{enumerate}
\section{Changelog}
\begin{enumerate}
    \item Adopted: Aug 5, 2020
\end{enumerate}
\end{document}
